### 2015-07-07 other-support/lofstead-cp.tex
fixed C and P

%\begin{tabbing}
%Project Title \hspace{5.5em}\=: \= Code Coupling for Scalability and Robust Data Analytics\\
%Source of Support           \>: \> Sandia National Laboratories LDRD \\
%Award Amount                \>: \> \$600K/year to SNL\\
%Period Covered              \>: \> 8/2014 -- 7/2017\\
%Investigator Commitment     \>: \> 0.5 FTE
%\end{tabbing}

>>>>

\begin{tabbing}
Project Title \hspace{5.5em}\=: \= SCADS: Scalable Deep Storage Hierarchy for Exascale Computing\\
Source of Support           \>: \> DOE Storage Systems and Input/Output for Extreme Scale Science\\
Award Amount                \>: \> \$176/year to SNL\\
Period Covered              \>: \> 10/2015 -- 9/2018\\
Investigator Commitment     \>: \> 0.25 FTE
\end{tabbing}
